---
title: "CaseStudyRamen"
author: "Krrish Ghindani"
date: "2024-09-16"
output: html_document
---

```{r}
#Loading the data frame
load("//Users/caterinaponti/Desktop/BSDS100/ramen.Rdata")

#summarize ramen data
summary(ramen)
```

## Exploratory Data Analysis

```{r }
#how many different brands in the data set
length(unique(ramen$Brand))
```

There are 355 diff erent brands in the data set.


```{r }
#turning Top.Ten data in a string column
ramen$Top.Ten <- as.character(ramen$Top.Ten, rm.na=TRUE)
#subsetting the year
years <- (substr(ramen$Top.Ten,1,4))

#printing unique values for year
print("Years with Top Ten data: ")

unique(years)
```
Top ten data are from years: 2016, 2015, 2013, 2014, 2012.

```{r }
#ramen brands from the United States
USA.brands <- which(ramen$Country =='USA','United States')

print("Ramen Brands from the US:")

unique(ramen$Brand[USA.brands])

```


```{r }
#subsetting to find place won by winning ramen
rating <- (substr(ramen$Top.Ten,6,7))
#selecting who won first place
top.1.indeces <- which(rating =='#1')
#getting the brands who won first place
top1.brands <- ramen$Brand[top.1.indeces]
#store top1.brands in a table
brand_counts <- table(top1.brands)
#look up for what elements in the list show up more than once
brands_more_than_once <- names(brand_counts[brand_counts >1])
brands_more_than_once
```

“Mama”, “MyKuali” and “Prima Taste” have won more than once fi rst place.

```{r }
#Aggregating by brands and calculating the mean of each brand
brand.stars.average <- aggregate(ramen$Stars, by = list(ramen$Brand), FUN =
"mean", na.rm=FALSE)
#maximum average
max_average_stars <- max(brand.stars.average$x, na.rm =TRUE)
print(max_average_stars)
```


```{r }
#top brands with maximum average rating
top_brand <- brand.stars.average[brand.stars.average$x == max_average_stars,]
print(top_brand$Group.1)
```
There are 27 brands whose average rating is the maximum rating.


```{r }
#loading libraries
library(ggplot2)
library(dplyr)
#lead dplyr package to use group by
```

```{r }
#grouping by country and style and selecting only countries whose count is greater than 10
packaging_data <- ramen %>% group_by(Country, Style) %>% summarise(Count = n()) %>% filter(Count >10)
```

```{r }
#plotting country against count filling bars by style
ggplot(packaging_data, aes(x = Country, y = Count, fill = Style)) + geom_bar(stat =
"identity", position ="stack") + 
  labs(title ="Ramen Packaging Styles by Country", x ="Country", y ="Count", fill="Packaging Style") +
scale_fill_brewer(palette ="Set3"
)
```
From the graph, it looks like in countries like Myanmar, Netherlands, Philippines, India and Nepal, the onlypackaging style for ramen is Pack. In countries like Indonesia, Canada, South Korea, USA, Thailand, Taiwan Bowlis the most popular packaging style. Tray is used as packaging style only in few countries like South Korea, Japanand the USA. In Mexico and Australia the only packaging used is the cup. From these observations, we canconclude that packaging is related in some way to which country it is from.


```{r }
#number of ramen entries for country
country_ramen_count <- ramen %>% group_by(Country) %>% summarize(Ramen_Count = n()) %>% arrange(desc(Ramen_Count))
#selectign the country which produces the most ramen
most_ramen_country <- country_ramen_count %>% slice(1)
print(most_ramen_country)
#Japan with 352 count

```
The country that produces most ramen is Japan.

```{r }
# Best ramen = best Stars average
# Group by Country and calculate average stars
country_average_stars <- ramen %>% group_by(Country) %>% summarize(Average_Stars = mean(Stars, na.rm =
TRUE
)) %>% arrange(desc(Average_Stars))
# Find the country with the highest average stars
best_country <- country_average_stars %>% slice(1)
print(best_country) #best country is Brazils
```
The fi rst way we thought about best ramen is by selecting which country had the highest average of stars fromthe ramen produced. It turn out Brazil with an average of 4.35 produces the “best” ramen. This answer diff ersfrom the country which produces most ramen: Japan.

```{r }
#Another way we thought about "best" ramen
#Best Ramen - country with most nominees in top 10
top.brand <- ramen$Brand[top.1.indeces]
top.countries <- ramen$Country[top.brand]
# countries in top 10 multiple times table with count
country_counts <- table(top.countries)
most_frequent_country <- names(which.max(country_counts))
most_frequent_country

```

Another way we thought about “best” ramen is by defi ning it as the the ramen with most nominee in the top 10. Inthis case, the country that makes best ramen is Japan. This answer is the same as the country which producesmost ramen!


```{r}
library('ggplot2')
library('tidyr')
#for drop_na() function
#more than 20 as count of style
saltiness <- ramen %>% drop_na() %>% group_by(Style, na.rm=TRUE)
#boxplot of Style and percent salt
ggplot(saltiness, aes(x = Style, y = perc_salt)) + geom_boxplot()
```

We can observe the distribution of percentage of salt for each packaging style. Cups, Packs, Trays andBowls have the highest percentage of salt. Cans, Bars and Boxes have a settled percentage of salt.

```{r}
# Filter ramen styles with more than 20 counts and perc_salt greater than 18
more_than_18 <- ramen %>% drop_na() %>% group_by(Style) %>% filter(n() > 20 & perc_salt > 18 )
#plot percent of salt by country
qplot(x = perc_salt, data=more_than_18, colour = Country)
```

In this visualization, we can observe how the percentage of salt for each country is well distributed whenlooking at high percentage of salt. For the highest levels of salt, Australia, Japan, and the US seem todominate.

```{r}
#percent of salt by Style and country
qplot(x = perc_salt, data=more_than_18, facets = .~Style, colour = Country)

```
In this graph we can observe which country has the highest levels of salt based on packaging styles.

```{r}
#plot percent of salt agaist star rating
qplot(perc_salt, Stars, data = ramen) + geom_smooth(method=lm)
```

From this plot, we can notice that as the percentage of salt increases the star rating increases as well.

```{r}
# Scatter plot of perc_salt vs Stars, colored by Style
qplot(perc_salt, Stars, data=ramen, color=Style)

```
From this visualization we can observe that Pack, Tray and Bowls have the highest percent of salt. Pack, Cup,and Bowl appear in the lowest percentage of salt. In general, all packaging styles seem to be equally distributedbetween all the percentages of saltiness.

```{r}
#plot of percent of salt and country
qplot(perc_salt, Country, data=ramen)
```

From this visualization we can observe how countries like China, Hong Kong, United States, Japan and Taiwanreach the highest of percentages of salt. UK, Canada, Colombia, Estonia, and Singapore tend to use smallerpercentages of salt.

```{r}
summary(ramen$perc_salt)
```


```{r}
#creating a subset of more than 22 percent salt
more_than22_salt <- ramen %>% filter(perc_salt >22)
#plotting countries with more than 22% of salt and adding Style
ggplot(more_than22_salt, aes(x = Country, y = perc_salt, fill = Style)) + geom_bar(stat ="identity", position ="stack") + 
theme(axis.text.x = element_text(angle = 90)) + 
labs(title ="Ramen Packaging Styles by Country", x ="Country", y ="Count", fill ="Packaging Style") + 
scale_fill_brewer(palette ="Set3")

```
We can observe which countries have the highest percentage of salt (top 10) and which packaging style are mostpopular in these countries. We can observe that packaging styles like Bowls, Cups and Packs have the highestpercentage of salt (higher than 22 percent).

```{r}
# Filter the top 10 brands
top_brands <- ramen %>% 
  count(Brand) %>% 
  top_n( 10, n) %>% 
  pull(Brand)
# plot percentage of salt by brand
ggplot(ramen %>% filter(Brand %in% top_brands), aes(x = Brand, y = perc_salt)) + geom_boxplot() + labs(title = "Distribution of Salt Percentage by Top 10 Ramen Brands", x ="Brand", y ="Percentage of Salt"
)
```
From this visualization we can observe that the top 10 brands (greater brand count) tend to use higherpercentages of salt.

```{r}
#loading libraries
library(tidyr)
library(stringr)
```


```{r}
# Function to estimate saltiness based on keywords found in Variety variable
estimate_saltiness <- function(variety) {
  # Define keywords that indicate saltiness
  salt_words <- c("salt", "soy", "shoyu", "miso", "seafood", "fish", "shrimp", "crab")      
  salt_score <- sum(str_count(tolower(variety), salt_words))
  return(salt_score)
  }

# Add a new column for Saltiness based on the Variety
ramen <- ramen %>% mutate(Saltiness = sapply(Variety, estimate_saltiness))
# Get the top 10 countries with the most ramen varieties
top_countries <- ramen %>% count(Country) %>% top_n(10, n) %>% pull(Country)
# Create a violin plot for the distribution of saltiness in the top coumntries
ramen %>% filter(Country %in% top_countries) %>% ggplot(aes(x = Country, y = Saltiness, fill = Country)) + geom_violin() + labs(title =
"Distribution of Estimated Saltiness by Country", 
x ="Country",
y ="Estimated Saltiness"
)
```
Another way we evaluated saltiness is by looking for certain keywords present on Variety. We can observe thatcountries like USA, Taiwan, Singapore and Japan have the highest percentage of estimated saltiness based onVariety


One way to break down the ramen in 5 collection is by salt percentage levels.

```{r}
#break down ramen into 5 collections of “similar” ramens
# Let's create 5 categories based on Stars rating and perc_salt
max(ramen$perc_salt)

```


```{r}
min(ramen$perc_salt)
```


```{r}
ramen$Collection <- ifelse(ramen$perc_salt <=5, "Very Low Salt",          ifelse(ramen$perc_salt > 5 & ramen$perc_salt <= 10, "Low Salt", ifelse(ramen$perc_salt >10 & ramen$perc_salt <=15,"Average Salt", ifelse(ramen$perc_salt >15 & ramen$perc_salt <=20, "High Salt", ifelse(ramen$perc_salt >20 & ramen$perc_salt <= 25, "Premium High Salt", "Ultra Premium High Salt"
))))) 
category_counts <- table(ramen$Collection)
#Plotting percent of salt and stars and coloring by collection (level of saltiness)
qplot(x = perc_salt, y = Stars, data = ramen, color = Collection)

```
From this plot we can observe how highest levels of salt lead to higher star ratings.


```{r}
#Analyzing only the Premium High Saltiness
premium_high_salt <- ramen %>% filter(Collection ==
"Premium High Salt")
premium_high_salt$Style <- as.factor(premium_high_salt$Style)
#boxplot of style and stars of only premium high salt
qplot(x = Style, y = Stars, data = premium_high_salt) + geom_boxplot()
```
This visualization of the premium level of salt shows us how distributed are the stars ratings based on packagingstyles. As seen previously in other visualizations, bowls, cups and packs have higher percent of salt and higherstar ratings.

```{r}
#loading libraries
library('readr')
```

```{r}
#Another way to break down our data set in 5 categories is based on the star rating
ramen$Stars <- as.numeric(ramen$Stars)
ramen <- ramen %>%
#break down n 5 categories based on ratings
  mutate(Collection = case_when( Stars >=4.5 ~ "Premium", 
                               Stars >=4 & Stars <4.5~"High Quality", 
                               Stars >=3.5 & Stars <4~"Good",
                               Stars >=3 & Stars <3.5 ~ "Average",
                               Stars < 3 ~ "Very Low"
                               ))

#grouping by collection (satr rating)
collection_summary <- ramen %>% group_by(Collection) %>% summarize( Count = n(), AvgStars = mean(Stars, na.rm =TRUE), TopCountries = paste(names(sort(table(Country), decreasing =TRUE)[1:3]), collapse =", "), TopStyles = paste(names(sort(table(Style), decreasing =TRUE)[1:2]), collapse =", "))
#printing collections summary
print(collection_summary)
```

```{r}
#plotting Collections against stars by collection
ggplot(ramen, aes(x = Collection, y = Stars, fill = Collection)) + geom_boxplot() + labs(title = "Ramen Ratings by Collection", x ="Collection", y ="Stars") + theme_minimal() + theme(axis.text.x = element_text(angle =45, hjust =1
))
```


```{r}
ramen %>% group_by(Collection, Country) %>% summarize(Count = n()) %>% group_by(Collection) %>% top_n(5, Count) %>% ggplot(aes(x = reorder(Country, Count), y = Count, fill = Collection)) + geom_col() + facet_wrap(~Collection, scales ="free_y") + coord_flip() + labs(title = "Top Countries in Each Ramen Collection", x ="Country", y ="Count"
)
```
From the above visualization, we can observe that Japan has the highest best ratings. USA has the most average and very low ratings. Furthermore, USA ramen’s ratings show up in all ratings categories Very Low, Average,Good, High Quality and Premium.


```{r}
#define a threshold
salt_threshold <- mean(ramen$perc_salt, na.rm =TRUE)
salt_threshold <-20
#filter higher than salt_threshold and equal to 5 stars
top_stars_high_salt <- ramen %>% filter(Stars == 5 & perc_salt > salt_threshold)
#top Variety with higher concentration of salt and stars rating
unique_varieties <- unique(top_stars_high_salt$Variety)
print(unique_varieties)
```
As observed in visualization #9, higher level of saltiness will lead to higher star ratings. Here we combined starsrating = 5 to greater than 20 percent level of saltiness and we got 12 best performing ramen Variety

```{r}
#summary statistics
summary_stats <- top_stars_high_salt %>% summarize( mean_salt = mean(perc_salt, na.rm =TRUE), min_salt = min(perc_salt, na.rm =TRUE), max_salt = max(perc_salt, na.rm =TRUE), count = n() )
print(summary_stats)

```
This is a summary statistics for top stars ramen with higher tnan 20 percentage of salt. Average percentage of saltis 20.50882.

```{r}
# Create a plot of salt percentage for the top varieties
ggplot(top_stars_high_salt, aes(x = Variety, y = perc_salt)) + geom_boxplot() + labs(title ="Salt Percentage of Top-Rated Ramen Varieties", x ="Ramen Variety", y =
"Percentage of Salt") + theme(axis.text.x = element_text(angle =45, hjust =1))

```

These are the top ramen varieties and their respective percentage of salt. As we observed in previous visualizations, higher salt percentages tend to lead to higher ratings and overall better performance. These 12varieties have high star ratings (5) and a high level of saltiness, which, as we observed earlier, correlates with better ratings. Therefore, the next best variety should likely fall within the range of these 12 varieties and have asalt percentage around 20.51%.


